---
title: "Multiple predictors"
author: "Cassie Gurbisz"
date: "4/5/2022"
output: html_document
---

```{r}
library(tidyverse)
library(tidymodels)
```

Load the crickets dataset, which includes rate of cricket chirps per minute, ambient temperature (deg C), and cricket species. 
```{r}
data(crickets)
```

1. Fit a model called `temp_sp_rate_fit` that predicts `rate` as a function of `temp` and `species`. Include an interaction term. 
```{r temp_sp_rate_fit}

```

2. Examine the model estimates and adjusted R2. Write the equation of the model and note the adjusted R2. 
```{r temp_sp_rate_fit-stats}

```

rate = -11.0 + 3.75 x temp - 4.35 x speciesO. niveus - 0.234 x temp x speciesO. niveus

3. Write the equation for just O. exclamationis.

rate = -11 + 3.75 x temp 

4. Write the equation for just O. niveus.

rate = -15.35  + 3.516 x temp

5. Create a plot of rate vs temp, with points colored by species. Add the regression lines for each species using the augmented model fit output.
```{r plot_fit}

```

5. Fit a model called `temp_sp_rate_fit2` that predicts `rate` as a function of `temp` and `species` without an interaction term. Look at the model estimates and R2 for both models. Which is the more parsimonious model (`temp_sp_rate_fit` or `temp_rate_fit`)?
```{r temp_rate_fit}

```

6. Create a plot of rate vs temp, with points colored by species. Add the regression lines for each species using the augmented model fit output.
```{r plot_fit2}

```

